\chapter{Discussion of results}
In this project a distributed Blackjack game has been developed that fulfills the requirements. The implementation uses the regular game rules.

In the implementation a dealer and a player has been developed. Multiple players can join a game with a single dealer. Multiple tables/dealers can run simultaneously. The players and dealers only communicate through an event service. This decouples in space, flow and time.

The decoupling in time was achieved by implementing a message queue on the event service. Furthermore time outs were used such that players and dealers do not have to wait for a disconnected player.

Low coupling between dealers and players makes it easy to modify and extend them independently.

The Publish/Subscribe pattern was implemented with topic-based communication. This made it easy to implement the current solution where different tables has different topic names. The players and dealers could then subscribe to a specific table.

Another solution could have been to use content-based subscription, where a dealer would subscribe to bets and players would subscribe to cards. This solution was not chosen, because it would be difficult to distinguish between different dealers and thereby more difficult to have multiple tables.

Additional patterns could have been used in the final solution such as the Acceptor/Connector pattern and the Leader/Followers pattern. The Acceptor/Connector pattern could have decoupled connection initialization and processing. It is important to note that this would also have introduced more complexity. Using the pattern would still enable for an easier change of transport layer protocol for example to TCP.

Leader/Followers pattern could have been used to process background tasks, this could be on the consumer side of the message queue to publish messages to the designated clients.

In the development, the focus was on creating a fully functional Blackjack game with design patterns from the course. To make sure this could be done within the time constrain no more patterns were used in the final solution.